Bow shocks, bow waves, and dust waves

### 2019-01-15 papers/Papers1234/dusty-bow-wave.tex
Finish abstract (still need to cut 20 words)

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Dust waves and bow waves result from the action of a star's
  radiation pressure on a stream of dust grains that is flowing past
  it.  They are an alternative mechanism to hydrodynamic bow shocks
  for explaining the curved arcs of infrared emission seen around some
  stars.  We develop simple models for the combined effects of
  radiation and stellar winds on an ambient flow in the case where gas
  and grains are perfectly coupled. We find that wind-supported bow
  shocks predominate when the ambient density is low
  (\(\ltae \SIrange{100}{1000}{cm^{-3}}\)) for a broad class of
  stellar parameters.  At higher densities, radiation-supported bows
  can form, tending to be optically thin bow waves in the case of B
  stars, or optically thick bow shocks in the case of early O stars.
  We further investigate the dynamics of dust grains when the
  radiation field is sufficiently strong to overcome the collisional
  coupling between grains and gas, showing that this occurs at a
  \textit{rip-point}, where the ratio of radiation pressure to gas
  pressure exceeds a critical value (\(P\rad/\Pgas > 1000\)).

\end{abstract}

>>>>

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Dust waves and bow waves result from the action of a star's
  radiation pressure on a stream of dusty plasma that flows past it.
  They are an alternative mechanism to hydrodynamic bow shocks for
  explaining the curved arcs of infrared emission seen around some
  stars.  When gas and grains are perfectly coupled, for a broad class
  of stellar parameters, wind-supported bow shocks predominate when
  the ambient density is below \SIrange{100}{1000}{cm^{-3}}.  At
  higher densities radiation-supported bows can form, tending to be
  optically thin bow waves around B~stars, or optically thick bow
  shocks around early O~stars.  The radiation field is sufficiently
  strong to overcome the collisional coupling between grains and gas
  at a \textit{rip-point}, where the ratio of radiation pressure to
  gas pressure exceeds a critical value of roughly 1000.  When the rip
  point occurs outside the hydrodynamic bow shock, a separate dust
  wave may form, decoupled from the gas shell, which can either be
  drag-confined or inertia-confined, depending on the stream density
  and relative velocity.  In the drag-confined case, there is a
  minimum stream velocity of roughly \SI{60}{km.s^{-1}} that allows a
  steady-state stagnant drift solution for the dust wave apex.  For
  lower relative velocities, the dust dynamics close to the axis
  exhibit a limit cycle behavior (rip and snap back) between two
  different radii.  Strong coupling of charged grains to the plasma's
  magnetic field can modify these effects, but for a quasi-parallel
  field orientation the results are qualitatively similar. For a
  quasi-perpendicular field, on the other hand, the formation of a
  decoupled dust wave is strongly suppressed.
\end{abstract}
